---
title: "Population, Samples, and Estimates"
output: html_notebook
---

First step of statistical inference is to find population you are interested in
```{r}
library(downloader)
url <- "https://raw.githubusercontent.com/genomicsclass/dagdata/master/inst/extdata/mice_pheno.csv"
filename <- "mice_pheno.csv"
download(url,destfile=filename)
dat <- read.csv(filename)
```

access the population values to compute size of the control population. m is 225
```{r}
library(dplyr)
controlPopulation <- filter(dat,Sex == "F" & Diet == "chow") %>% 
  select(Bodyweight) %>% unlist
length(controlPopulation)
```

Compute the size of high fat diet population. n is 200
```{r}
hfPopulation <- filter(dat,Sex == "F" & Diet == "hf") %>%  
  select(Bodyweight) %>% unlist
length(hfPopulation)
```
define summaries of interest for these populations, such as the mean and variance using statistical inference with samples since we dont have access to the entire population

Samples with capital letters



```{r}
library(downloader) 
url <- "https://raw.githubusercontent.com/genomicsclass/dagdata/master/inst/extdata/mice_pheno.csv"
filename <- basename(url)
download(url, destfile=filename)
dat <- read.csv(filename) 
```
remove the lines that contain missing values:
```{r}
dat <- na.omit(dat)

```
1.Use dplyr to create a vector x with the body weight of all males on the control (chow) diet. What is this population’s average?

I need to know the size of all males in control to create the appropriate vector size
```{r}
control_males <- dat %>% filter(Sex == "M", Diet == "hf") 
length(control_males[])

```
```{r}
n = 579
x <-  vector("numeric",n)
x <- dat
mean(x[])
```












