---
title: "R Notebook"
output: html_notebook
---

Try executing this chunk by clicking the *Run* button  *Ctrl+Shift+Enter*. 
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.
When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

Setup
```{r}
install.packages("rafalib")
library(downloader) 
library(dplyr)
library(rafalib)
url <- "https://raw.githubusercontent.com/genomicsclass/dagdata/master/inst/extdata/femaleControlsPopulation.csv"
filename <- basename(url)
download(url, destfile=filename)
x <- unlist( read.csv(filename) )
```

The distribution of this data:
```{r}
hist(x) %>% abline(v = mean(x),col = "red",lwd = 3)
```
1. What is the average of these weights?
```{r}
mean(x)

```

2. What is the absolute value of difference between sample mean and population mean? (Set seed to 1 and random sample of 5)
The Sampling Error of pop. mean of 23.89 and Sample Mean of 23.56 is .3293
```{r}
set.seed(1)
abs(mean(sample(x,5)) - mean(x))

```
3. Calculate the sample error but with a different seed of 5.
The sampling error of the pop. mean of 23.89338 and sample mean of 23.512 is 0.3813778
```{r}
set.seed(5)
abs(mean(sample(x,5))-mean(x))
```
4. The seed changes the sampling error results because the avg of the samples is a random variable that is different


5. Take a random sample of 5 mice 1,000 times. Save these averages
```{r}
set.seed(1)
n <- 1000
null5 <- vector("numeric",n)
for(i in 1:n){
  null5[i] <- mean(sample(x,5))
}
```
Null Hypothesis: What percent of 1,000 avg is more than 1 ounce away from the average of x ?
*Curious that i dont get a logical response from >

```{r}
mean(abs(null5 - mean(x)) > 1)
```
6. redo the sample from 1,000 to 10,000. Set the seed at 1, then using a for-loop take a random sample of 5 mice 10,000 times. Save these averages. What percent of these 10,000 averages are more than 1 ounce away from the average of x ?
```{r}
set.seed(1)
k <- 10000
null50 <- vector("numeric",n)
for(i in 1:n){
  null50[i] <- mean(sample(x,5))
}
```

```{r}
mean(abs(null50 - mean(x)) > 1)
```

```{r}
mypar(1,2) # plot histograms
hist(null5)
hist(null50)
```


For the last set of averages, the ones obtained from a sample size of 50, what percent are between 23 and 25?
```{r}
mean((null50 >=23) & (null50 <= 25))
```




